The limits of self commitment and private paternalism \thanks{}

### 2022-02-11 Tables/Attrition.tex
annualize apr and effects in std deviations

% Table generated by Excel2LaTeX from sheet 'Attrition'
\begin{tabular}{lccccccccc}
\toprule
      & \multicolumn{9}{c}{Attrition Table} \\
\midrule
      &       &       &       &       & \multicolumn{2}{c}{Fee arms} & \multicolumn{2}{c}{Promise arms} &  \\
\midrule
\midrule
      & \multicolumn{1}{p{4.045em}}{Overall} & \multicolumn{1}{p{3.5em}}{Pre-exp} & \multicolumn{1}{p{3.365em}}{p-value} & \multicolumn{1}{p{3.275em}}{Control} & \multicolumn{1}{p{4.775em}}{Forced-fee} & \multicolumn{1}{p{3em}}{Choice} & \multicolumn{1}{p{3em}}{Forced} & \multicolumn{1}{p{3em}}{Choice } & \multicolumn{1}{p{3.365em}}{p-value} \\
\midrule
\midrule
Number of branch-day pawns & 34    & 36    & 0.71  & 31    & 31    & 37    & 32    & 34    & 0.38 \\
      & (0.8) & (1.3) &       & (2.2) & (2.3) & (2.6) & (2.4) & (1.7) &  \\
Survey response rate &       & 0.78  &       & 0.77  & 0.75  & 0.77  & 0.8   & 0.79  & 0.46 \\
      &       & (0.01) &       & (0.02) & (0.03) & (0.02) & (0.02) & (0.02) &  \\
\% ended up pawning &       & 0.98  &       & 0.97  & 0.96  & 0.97  & 0.98  & 0.99  & 0.03 \\
      &       & (0.003) &       & (0.004) & (0.008) & (0.006) & (0.004) & (0.003) &  \\
Number of branch-days & -     & 180   &       & 84    & 80    & 93    & 68    & 82    &  \\
\midrule
Obs   & 13534 & 180   &       & 2585  & 2465  & 3406  & 2143  & 2755  &  \\
\bottomrule
\bottomrule
\end{tabular}%

>>>>

% Table generated by Excel2LaTeX from sheet 'Attrition'
\begin{tabular}{lccccccc}
\toprule
      & \multicolumn{7}{c}{} \\
\midrule
      &       & \multicolumn{3}{c}{Commitment arms} & \multicolumn{3}{c}{Soft arms} \\
\midrule
\midrule
      & Control & Forced & Choice & p-value & Forced & Choice  & p-value \\
\midrule
\midrule
Number of branch-day pawns & 31    & 31    & 37    & 0.16  & 32    & 34    & 0.57 \\
      & (2.2) & (2.3) & (2.6) &       & (2.4) & (1.7) &  \\
Survey response rate & 0.77  & 0.75  & 0.77  & 0.73  & 0.8   & 0.79  & 0.44 \\
      & (0.02) & (0.03) & (0.02) &       & (0.02) & (0.02) &  \\
\% ended up pawning & 0.97  & 0.96  & 0.97  & 0.59  & 0.98  & 0.99  & 0.11 \\
      & (0.004) & (0.008) & (0.006) &       & (0.004) & (0.003) &  \\
\midrule
Obs   & 2585  & 2465  & 3406  &       & 2143  & 2753  &  \\
\bottomrule
\bottomrule
\end{tabular}%

### 2022-02-11 donde.tex
annualize apr and effects in std deviations

\title{The limits of self-commitment and private paternalism \thanks{We want to thank Mauricio Romero and Anett John for advice and encouragement. Ricardo Olivares, Gerardo Melendez, and Alonso de Gortari provided excellent research assistance and Erick Molina helped with formatting. Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, David Laibson, Aprajit Mahajan, Matt Rabin, Charlie Sprenger, and seminar participants at ITAM provided valuable feedback.}}
\author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira   \thanks{Seira: ITAM, enrique.seira@gmail.com (corresponding author); McIntosh:  University of California San Diego, ctmcintosh@ucsd.edu; Meza: University of California at Berkeley, isaac.meza@berkeley.edu; Sadka: ITAM, jsadka@itam.mx} }
\date{This draft:  \today \\[2 cm]}

@@

\vspace{.2in}
\noindent \textbf{Treatment Arms.} Randomization was done at the branch-day level. Each day we randomly assigned which types of contracts were on offer that day in the branch, and therefore which contract the client signed.  We have 5 different experimental arms:

@@

The study is subject to two potential forms of attrition.  The more serious is that clients would change their pawning decisions in response to the treatment arms.  If this were the case, our study would still recover internally valid estimates of the impacts of the treatment arms for the lender, but would not provide \textit{ceteris paribus} impacts on a comparable pool of individuals. We anticipated this possibility and trained appraisers to say --that whatever was the contract that day-- it was the only available contract for an undetermined amount of time.   Because we do not observe refusals directly, we address this issue by examining the number of borrowers per day, and the number of borrowers who were surveyed but then did not pawn.

@@

Our enumerators informed us that potential clients rarely left the branch without pawning, and that it was even less common that they did so when hearing about monthly installments. It turns out that only \hl{XXX\%} of those surveyed ended up not pawning and appearing in the administrative data. Lender P also never complained to us that our different treatments were hurting sales. The data support this story as well. First, we cannot reject that the number of pawns per branch-day is the same across arms (Panel A). Panel C shows that about 98\% of people who answered our baseline survey also pawned, and that this ratio is balanced across arms. Second, not only are the number and shares of pawns the same across arms, but also the characteristics of clients and their pawned pieces are statistically the same across arms. Panel A of Table \ref{SS} tests this with administrative data, while Panel B tests it using baseline survey data for those that pawned, and Panel C does it without conditioning on pawning. %The difference is that Panel B compares people that pawned, while {Panel C uses clients that did not pawn.} 
Third, the characteristics of those who pawned before our experiment began are statistically the same as those during the experiment, as documented in the first and second column of Panel C.

@@

A second form of attrition would be differential refusal to answer the survey questions.  This is less of a concern, both because the survey was done before treatment status was revealed, and because we still have institutional data for the universe of borrowers.  Nonetheless, to test the internal validity of any measures in the study that use survey data, we test for differential attrition here as well.

@@

\textcolor{red}{Need to build Attrition Table}

@@

\subsection{Balance in the Experimental Sample}
Table \ref{SS} presents summary statistics for the sample of actual borrowers across arms, and illustrates that randomization worked to achieve balance across clients in the different experimental arms. Panel A describes variables from the administrative data. The average loan size is \$2197 MXN (\$105 USD). The average number of pawns per day per branch is 34. Only 42\% of clients recover their pawn. Even those that recover their pawn tend to pay it back at the last moment, with only 40\% paying before the 90th day.

Panel B reports stats from our survey data. 73\% of clients are women, with an average age of 43 years; 66\% of them have completed high school or more, and 90\% have pawned before, so that our sample has mostly experienced borrowers. Finally the subjective probability of recovery is close to 93\% on average, which contrasts with the 51 points lower actual recovery. Borrowers seem to be highly overconfident on average. The average subjective value they report for the pieces is 3069 MXN, much larger than the average appraised gold value of 2197 MXN. %This makes it inefficient for them to lose it.

\textcolor{red}{Imbalance in survey data needs to be addressed?}

@@

We now present the core experimental results, illustrating how the Commitment Choice and Forced Commitment arms differ from the control.

@@

The Intention to Treat (ITT) results are very clear:  giving clients the option of choosing commitment is not effective, and forcing them into the commitment contract is.  Choice does \textit{not} lead to lower financial cost compared to the status-quo contract. Nor does it lead to higher pawn recovery. The hollow circles in Figure \ref{fc_pro4}(a) show zero average effects for the different definitions of financial cost analogous to the ones described above. Figure \ref{fc_pro4}(b) shows further that the null effect happens for the 15$^{th}$, 25$^{th}$, 50$^{th}$ 75$^{th}$, and 85$^{th}$ percentiles.\footnote{The few clients that chose the Commitment contract (the solid black squares) do enjoy cost savings of 1005 MXN, which compares favorably to the 304 MXN in the Forced arm (as a fraction of the loan the numbers are 41.5\% and 12.5\%), but this combines the selection and treatment effects.} %Figure \ref{heterogeneous_te_4} plots the distribution of treatment effects and finds that the distribution offering choice actually \textit{increased} financial cost and default for about half of clients compared to being assigned the status-quo contract. Those tended to be the less economically vulnerable and more educated, {women}, and those whose family typically asks them for money.
Figure \ref{fc_pro4}(c) finds null effects for pawn recovery. Consistent with these findings, Figure \ref{reincidence} finds no effect on repeat purchases for the Commitment Choice group.

\vspace{.2in}
\noindent \textbf{Financial Cost.} Figure \ref{fc_pro2}(a) reports $\beta$ coefficients and their 95\% confidence interval from estimating equation (\ref{basic_reg}) using different definitions of financial cost. The leftmost coefficient corresponds to plugging into the formula of section \ref{FC_def} the appraised gold value of the pawned piece. The second coefficient uses the subjective value of the pawn instead. In both cases we find that being assigned to the Forced Commitment commitment contract causes a large reduction in the financing cost the client incurred, of 9.4\% (\$297) under the first definition and 13.2\% (\$472) under the second one. That is, we find that \textit{charging} clients a late payment decreases total \textit{fee-inclusive} financing cost.

@@

@@

\vspace{.2in}
\noindent \textbf{Is there positive selection on treatment effects?} The previous exercise consisted of extrapolating treatment effects from the no-choice arms to the choice arm. Here we do the reverse. First, we estimate a flexible model of take-up of the fee commitment contract \textit{in the choice arm} using \textcolor{red}{gradient boosting classification}\footnote{\textcolor{red}{Results are robust to other classification methods like Random Forest, SVM, etc.}} and obtain for a client with characteristics $x_i$ a \textcolor{red}{calibrated} probability $P(x_i)$ of choosing the Forced Commitment contract. We then use this model to predict the counterfactual probability of a client with characteristics $x_j$ choosing the fee-commitment contract \textit{in the no choice-arms} if she would have been given the choice, what we call $\widehat{P(x_j)}$.\footnote{Our \textcolor{red}{gradient boosting} take-up model has a good out-of-sample fit with an out-of-sample AUC of \colorbox{yellow}{0.85}. (accuracy 97\% in-sample and 90\% out-of-sample)} Second, armed with this prediction in the forcing arms, we can ask the following: is it true that people with larger Forced Commitment contract treatment effects (i.e. more cost savings) are more likely to have demanded the Forced Commitment contract if choice had been given to them?

@@

Let $Z_i$ be the observed, randomly assigned experimental allocation, where $Z_i=0$ denotes the control arm, $Z_i=1$ denotes the forced-fee arm, and $Z_i=2$ is the choice arm.  Let $T_i$ be the unobserved choice type. $T_i=0$ when individual $i$ does not choose commitment  given the choice and $T_i=1$ when chooses commitment given the choice. Finally, $D_i = Z_i\times \mathds{1}(Z_i\neq 2) + T_i\times \mathds{1}(Z_i=2)$ is the observed treatment indicator, and $Y(d,z)$ is the potential outcome function for $d=0,1$, and $z=0,1,2$.

@@

@@

\begin{figure}[H]
     \caption{Quantile regressions}
    \label{qregs}
    \begin{center}
    \begin{subfigure}{.45\textwidth}
      \caption{Financial cost (in MXN)}
        \centering
        \includegraphics[width=\textwidth]{Figuras/qreg_fc_admin.pdf}
    \end{subfigure}
     \begin{subfigure}{0.45\textwidth}
    \caption{APR}
       \centering
      \includegraphics[width=\textwidth]{Figuras/qreg_eff_cost_loan.pdf}
    \end{subfigure}
    \end{center}
         \scriptsize
     This figure plots the effects on different quantiles (15th, 25th, 50th, 75th, 85th percentile) of the distribution of financial cost, and APR, for the Forced-fee and Choice arms.
      %\footnotesize{ } \textit{Do file: }  \texttt{main\_qreg.do}
\end{figure}

@@

\begin{figure}[H]
    \caption{The effect of choice between fee-commitment and status quo}
    \label{fc_pro4}
    \begin{center}
    \begin{subfigure}{0.45\textwidth}
        \caption{Financial cost}
        \centering
        \includegraphics[width=\textwidth]{Figuras/fc_te_pro_4.pdf}
    \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
        \caption{Financial Cost (quantile reg)}
        \centering
        \includegraphics[width=\textwidth]{Figuras/fc_quantile_pro_4.pdf}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}

@@

    \end{center}
     \scriptsize   This figure asks whether it is the case that people with larger causal benefits from the Forced Commitment contract would be more likely to select that contract. To do this we proceed in two steps. First we estimate a flexible model of take-up of the fee commitment contract \textit{in the choice arm} using gradient boosting classification, and from this model obtain a probability $P(x_i)$ of choosing the Forced Commitment contract for a client with characteristics $x_i$. We extrapolate this model to clients in the Forced Commitment arm to estimate what would they have chosen if we had given them choice. We plot $\widehat{P(x_i)}$ in the X-axis using a binscatter that splits the X-axis in 100 percentile bins. The Y-axis plots the heterogeneous treatment effects of the (a) effective cost/loan benefit and (b) repayment, averaged for the respective x-axis bin. Positive assortative selection would mean a negative relationship: those who benefit more by treatment and lose the pawn less are \emph{less} likely to choose it. 
          %\footnotesize{ \textit{Do file: }  \texttt{benefit\_choice.do}}
\end{figure}

@@

>>>>

\title{The limits of self-commitment and private paternalism \thanks{We want to thank Mauricio Romero and Anett John for advice and encouragement. Ricardo Olivares, Gerardo Melendez, and Alonso de Gortari provided excellent research assistance and Erick Molina helped with formatting. Jose Maria Barrero, Francis DiTraglia, Andrei Gomberg, Emilio Gutierrez, David Laibson, Aprajit Mahajan, Matt Rabin, Charlie Sprenger, and seminar participants at ITAM provided valuable feedback.}}
\author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira   \thanks{Seira: ITAM, enrique.seira@gmail.com (corresponding author); McIntosh:  University of California San Diego, ctmcintosh@ucsd.edu; Meza: University of California at Berkeley, isaac.meza@berkeley.edu; Sadka: ITAM, jsadka@itam.mx} }
\date{This draft:  \today \\[2 cm]}

@@

\vspace{.2in}
\noindent \textbf{Treatment Arms.} Randomization was done at the branch-day level. Each day a computer randomly assigned which types of contracts were on offer that day in the branch, and therefore which contract the client signed.  We have 5 different experimental arms:

@@

The study is subject to two potential forms of attrition.  The more serious is that clients would change their pawning decisions in response to the treatment arms.  If this were the case, our study would still recover internally valid estimates of the impacts of the treatment arms for the lender, but would not provide \textit{ceteris paribus} impacts on a comparable pool of individuals. We anticipated this possibility and trained appraisers to say --that whatever was the contract that day-- it was the only available contract for an undetermined amount of time.   Because we do not observe refusals directly, we address this issue by examining the number of borrowers per day.\footnote{Our enumerators informed us that potential clients rarely left the branch without pawning, and that it was even less common that they did so when hearing about monthly installments. Lender P also never complained to us that our different treatments were hurting sales. The data support this story as well.}

A second form of attrition would be differential refusal to answer the survey questions.  This is less of a concern, both because the survey was done before treatment status was revealed, and because we still have institutional data for the universe of borrowers.  Nonetheless, to test the internal validity of any measures in the study that use survey data, we test for differential attrition here as well.  A third way of examining attrition is to look at the fraction of borrowers who do respond to the survey and then do not end up taking a loan subsequent to completing the survey.

@@

Table \ref{attrition_table} presents tests for these core forms of attrition.  Most importantly, the top row shows that there is no difference between the Control and Forced Commitment arms in terms of the number of pawns per day, suggesting that there has been no differential refusal when borrowers were defaulted into the Commitment contract.  The Choice arm appears to have a somewhat larger number of borrowers than the Control arm, but given that there is no reason to think that we would have seen differential uptake for this arm (where the status quo contract is freely available) we view this as a chance occurrence.  The survey response rate is broadly similar across arms (about 77 percent) as is the fraction of those surveyed who then go on to take a loan (97 percent).

%First, we cannot reject that the number of pawns per branch-day is the same across arms (Panel A). Panel C shows that about 98\% of people who answered our baseline survey also pawned, and that this ratio is balanced across arms. Second, not only are the number and shares of pawns the same across arms, but also the characteristics of clients and their pawned pieces are statistically the same across arms. Panel A of Table \ref{SS} tests this with administrative data, while

@@

@@

@@

\subsection{Balance in the Experimental Sample}
Table \ref{SS} presents summary statistics for the sample of actual borrowers across arms, and illustrates that randomization worked to achieve balance across clients in the different experimental arms.

Panel A uses administrative data for the universe of borrowers in each arm, and shows that loan balances and the days on the week on which individuals pawned are comparable across arms.  The average loan size is \$2197 MXN (\$105 USD).

Panel B of Table \ref{SS} reports summary statistics across arms from our survey data. 73\% of clients are women, with an average age of 43 years; 66\% of them have completed high school or more, and 90\% have pawned before, so that our sample has mostly experienced borrowers. Finally the subjective probability of recovery is close to 93\% on average, which makes a stark contrast to the actual rate of recovery (42\%).  In other words, borrowers are highly overconfident on average. The average subjective value they report for the pieces is 3069 MXN, much larger than the average appraised gold value of 2197 MXN.  While this could arise either from overconfidence in valuation or from undervaluation by the lender, in any case it is \textit{prima facie} evidence that loss of the pawn should be undesirable relative to the quantity of liquidity leveraged by the asset.

Panel C repeats the exercise in Panel B, but now only for those borrowers answered the survey and then went on to take a loan.  Since we have aready shown that the attrition rate of borrowers after completing the survey was very low (3\% on average) it is unsurprising that these two panels are similar.  Overall, we find both the loan attributes and the survey attributes of borrowers to be similar across arms.  The experiment appears to have been successful in generating a balanced sample for analysis.

%Panel A describes variables from the administrative data.  The average number of pawns per day per branch is 34. Only 42\% of clients recover their pawn. Even those that recover their pawn tend to pay it back at the last moment, with only 40\% paying before the 90th day.

@@

We now present the core experimental results, illustrating how the Commitment Choice and Forced Commitment arms differ from the control.  This comparison is particularly illuminating on the role of self-selection in Commitment, because if this self-selection mechanism works perfectly (as it would in a Roy model with all hyperbolics sophisticated) then the Forced and Choice arms will have an identical effect.  Deviations between the impacts of these two arms therefore are implicitly a test of the optimatlity of the choices made in the choice arm.

@@

The Intention to Treat (ITT) results are very clear:  giving clients the option of choosing commitment is not effective, and forcing them into the commitment contract is.  Choice does \textit{not} lead to lower financial cost compared to the status-quo contract. Nor does it lead to higher pawn recovery.  Figure \ref{main_te} gives the standardized effect sizes (in standard deviations) of the two main study arms for three outcomes:  default, the financial cost of the loan, and the effective interest rate paid to acquire the borrowed capital.  Very clearly, the Forced arm is significant for all three outcomes, with very substantial treatment effects in magnitudes for default and APR, and the commitment arm is never significant.

\textcolor{red}{Include here table that has regressions from Eq. 1 underlying the figure above.}

\vspace{.2in}
\noindent \textbf{Detailed analysis of financial cost.} Figure \ref{fc_pro4} digs in more detail into the sources of variation underlying the main effects in Figure \ref{main_te}.   $\beta$ coefficients and their 95\% confidence interval from estimating equation (\ref{basic_reg}) using different definitions of financial cost. The leftmost coefficient corresponds to plugging into the formula of section \ref{FC_def} the appraised gold value of the pawned piece. The second coefficient uses the subjective value of the pawn instead. In both cases we find that being assigned to the Forced Commitment commitment contract causes a large reduction in the financing cost the client incurred, of 9.4\% (\$297) under the first definition and 13.2\% (\$472) under the second one. That is, we find that \textit{charging} clients a late payment decreases total \textit{fee-inclusive} financing cost.

@@

\textcolor{red}{Beginning of discussion on Quantile Effects:.}
The hollow circles in Figure \ref{fc_pro4}(a) show zero average effects for the different definitions of financial cost analogous to the ones described above.   Figure \ref{fc_pro4}(b) shows further that the null effect happens for the 15$^{th}$, 25$^{th}$, 50$^{th}$ 75$^{th}$, and 85$^{th}$ percentiles.\footnote{The few clients that chose the Commitment contract (the solid black squares) do enjoy cost savings of 1005 MXN, which compares favorably to the 304 MXN in the Forced arm (as a fraction of the loan the numbers are 41.5\% and 12.5\%), but this combines the selection and treatment effects.} %Figure \ref{heterogeneous_te_4} plots the distribution of treatment effects and finds that the distribution offering choice actually \textit{increased} financial cost and default for about half of clients compared to being assigned the status-quo contract. Those tended to be the less economically vulnerable and more educated, {women}, and those whose family typically asks them for money.
Figure \ref{fc_pro4}(c) finds null effects for pawn recovery. Consistent with these findings, Figure \ref{reincidence} finds no effect on repeat purchases for the Commitment Choice group.

@@

\vspace{.2in}
\noindent \textbf{Is there positive selection on treatment effects?} The previous exercise consisted of extrapolating treatment effects from the no-choice arms to the choice arm. Here we do the reverse. First, we estimate a flexible model of take-up of the commitment-fee contract \textit{in the choice arm} using \textcolor{red}{gradient boosting classification}\footnote{\textcolor{red}{Results are robust to other classification methods like Random Forest, SVM, etc.}} and obtain for a client with characteristics $x_i$ a \textcolor{red}{calibrated} probability $P(x_i)$ of choosing the Forced Commitment contract. We then use this model to predict the counterfactual probability of a client with characteristics $x_j$ choosing the fee-commitment contract \textit{in the no choice-arms} if she would have been given the choice, what we call $\widehat{P(x_j)}$.\footnote{Our \textcolor{red}{gradient boosting} take-up model has a good out-of-sample fit with an out-of-sample AUC of \colorbox{yellow}{0.85}. (accuracy 97\% in-sample and 90\% out-of-sample)} Second, armed with this prediction in the forcing arms, we can ask the following: is it true that people with larger Forced Commitment contract treatment effects (i.e. more cost savings) are more likely to have demanded the Forced Commitment contract if choice had been given to them?

@@

Let $Z_i$ be the observed, randomly assigned experimental allocation, where $Z_i=0$ denotes the control arm, $Z_i=1$ denotes the Commitment-fee arm, and $Z_i=2$ is the choice arm.  Let $T_i$ be the unobserved choice type. $T_i=0$ when individual $i$ does not choose commitment  given the choice and $T_i=1$ when chooses commitment given the choice. Finally, $D_i = Z_i\times \mathds{1}(Z_i\neq 2) + T_i\times \mathds{1}(Z_i=2)$ is the observed treatment indicator, and $Y(d,z)$ is the potential outcome function for $d=0,1$, and $z=0,1,2$.

@@

\begin{table}[H]
\caption{Determinants of Choice}
\label{det_choose}
\begin{center}
\scriptsize{\input{./Tables/determinants_choose.tex}}
\end{center}
 \scriptsize

%\textit{Do file: } \texttt{determinants\_choose.do}
\end{table}

\scriptsize {
\noindent 
}

@@

\begin{figure}[H]
     \caption{Several definitions of FC}
    \label{robustness_fc}
    \begin{center}
    \begin{subfigure}{0.75\textwidth}
        \centering
        \includegraphics[width=\textwidth]{Figuras/fc_robustness.pdf}
    \end{subfigure}
    \end{center}
    \scriptsize
    This figure shows treatment effects using several measures of cost. The first definition is our main definition of cost, which uses the appraised value of the pawn. The second definition uses the subjective (self-reported) value for the pawn. The third and fourth definition adds the travel cost for the treatment arms. We also compute APR versions of the above measures. 
    Finally, `APR - interests' is a version of the APR that doesn't include the interest that is mechanically saved by paying early since this is the piece of the commitment-fee contract that has a foregone liquidity cost for the borrower. The treatment effects are indicated in standard deviations, together with 95\% confidence intervals.
\end{figure}

\begin{figure}[H]
    \caption{Detailed comparison of Forced and Choice Commitment arms}
    \label{fc_pro4}
    \begin{center}
    \begin{subfigure}{0.45\textwidth}
        \caption{Financial cost}
        \centering
        \includegraphics[width=\textwidth]{Figuras/fc_te_pro_4.pdf}
    \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
        \caption{Financial Cost (quantile reg)}
        \centering
        \includegraphics[width=\textwidth]{Figuras/fc_quantile_pro_4.pdf}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}

\begin{figure}[H]
     \caption{Quantile regressions}
    \label{qregs}
    \begin{center}
    \begin{subfigure}{.45\textwidth}
      \caption{Financial cost (in MXN)}
        \centering
        \includegraphics[width=\textwidth]{Figuras/qreg_fc_admin.pdf}
    \end{subfigure}
     \begin{subfigure}{0.45\textwidth}
    \caption{APR}
       \centering
      \includegraphics[width=\textwidth]{Figuras/qreg_eff_cost_loan.pdf}
    \end{subfigure}
    \end{center}
         \scriptsize
     This figure plots the effects on different quantiles (15th, 25th, 50th, 75th, 85th percentile) of the distribution of financial cost, and APR, for the Commitment-fee and Commitment-choice arms.
      %\footnotesize{ } \textit{Do file: }  \texttt{main\_qreg.do}
\end{figure}

@@

@@

    \end{center}
     \scriptsize   This figure asks whether it is the case that people with larger causal benefits from the Forced Commitment contract would be more likely to select that contract. To do this we proceed in two steps. First we estimate a flexible model of take-up of the commitment-fee contract \textit{in the choice arm} using gradient boosting classification, and from this model obtain a probability $P(x_i)$ of choosing the Forced Commitment contract for a client with characteristics $x_i$. We extrapolate this model to clients in the Forced Commitment arm to estimate what would they have chosen if we had given them choice. We plot $\widehat{P(x_i)}$ in the X-axis using a binscatter that splits the X-axis in 100 percentile bins. The Y-axis plots the heterogeneous treatment effects of the (a) effective cost/loan benefit and (b) repayment, averaged for the respective x-axis bin. Positive assortative selection would mean a negative relationship: those who benefit more by treatment and lose the pawn less are \emph{less} likely to choose it. 
          %\footnotesize{ \textit{Do file: }  \texttt{benefit\_choice.do}}
\end{figure}

@@

\input{OA.tex}
